---
title: "Contig Lengths"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Analysis of contig lengths in the dovetail assembly

First read in the contig length data and add 

```{r}
total_genome_size <- 4009599824.0

contig_lengths <- read_table2("assembly_data/hmac_dovetail_assembly.lengths.txt", col_names = c("Contig","Length")) %>% 
  mutate(GenomeSize=cumsum(as.numeric(Length))) %>% 
  mutate(GenomeProportion=GenomeSize/total_genome_size) %>% 
  add_column(rank=1:nrow(contig_lengths))
```

A histogram of contig lengths reveals that the vast majority are small

```{r}
ggplot(contig_lengths,aes(x=Length)) + geom_histogram()
```

Plot cumulative genome size against a sorted list of contigs.  This helps think about a sensible length cut-off for short contigs and summarises the contiguity of the genome

```{r}
ggplot(contig_lengths,aes(x=as.numeric(rank),y=GenomeProportion)) + geom_line() 
```

```{r}
contig_lengths %>% filter(GenomeProportion>0.96) %>% count()
```
How much of the genome would we lose by removing contigs less than 50kb in size?.  This would remove about 5% of the assembly contained within 32342 contigs.

```{r}
cut_off <- 50000
100*(contig_lengths %>% filter(Length<cut_off) %>% pull(Length) %>% sum())/total_genome_size

contig_lengths %>% filter(Length<cut_off) %>% count()
```
